\LARGE \bf ***

### 2020-09-17 icra-2021.tex
stating the problem (1)

Mobile robots are increasingly used in a broad range of applications. The growing demand for autonomy of such devices challenges traditional methodologies, soliciting the development of new and unprecedented techniques. The presented approach proposes a \emph{mission-aware energy planning algorithm} that addresses the broader problem of increasing \emph{computational demands} and their relation to the robot's energy consumption and autonomy. The energy is varied by means of mission-specific parameters, the Quality of Service (QoS) of the onboard computations, and the trajectory explicit equations (TEEs) parameters. The approach ideally accounts for a mission extension by adapting the QoS and TEEs parameters as the robot batteries drain.

@@

Starting with a position $\mathbf{p}\in\mathbb{R}^3$ in the 3D Euler space, with respect to some inertial navigation frame $\mathcal{O}_W$, a guidance action--which allows the motion along the 3-axis--is built upon the direction to follow and derived using vector field~\cite{de2017guidance}. To define the direction to follow, we use generic continuously differentiable functions TEEs $\varphi:\mathbb{R}^3\rightarrow\mathbb{R}$, a mathematical abstraction representing the desired trajectory (being the function satisfied $\varphi(\mathbf{p})\rightarrow 0$ for all the points approaching such trajectory).

>>>>

Precision agriculture is rising in demand for reducing waste, costs, and resources while increasing outputs and utilization~\cite{hajjaj2014review}. Although researchers have satisfied some of these demands applying mobile robots in applications such as harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, more complex monitoring strategies--often implemented utilizing unmanned aerial vehicles (UAVs)--are usually required for preventing damage and ensuring better crop quality~\cite{puri2017agriculture}. Planning a mission for UAVs operating in such scenarios is a challenging task. It usually requires advanced levels of autonomy--with the UAV being required e.g., to inform its grounded counterparts of obstacles detected while flying--along with strictly limited energy budgets. The presented approach proposes a \emph{mission-aware energy planning algorithm} for UAVs for precision agriculture that addresses the broader problem of increasing \emph{computational demands} and their relation to the UAV's energy consumption and autonomy.

---

The energy is varied by means of mission-specific parameters, the Quality of Service (QoS) of the onboard computations, and the trajectory explicit equations (TEEs) parameters. The approach ideally accounts for a mission extension by adapting the QoS and TEEs parameters as the robot batteries drain.

@@

Starting with a position $\mathbf{p}\in\mathbb{R}^3$ in the 3D Euclidean space, with respect to some inertial navigation frame $\mathcal{O}_W$, a guidance action--which allows the motion along the 3-axis--is built upon the direction to follow and derived using vector field~\cite{de2017guidance}. To define the direction to follow, we use generic continuously differentiable functions TEEs $\varphi:\mathbb{R}^3\rightarrow\mathbb{R}$, a mathematical abstraction representing the desired trajectory (being the function satisfied $\varphi(\mathbf{p})\rightarrow 0$ for all the points approaching such trajectory).
